---
title: "A1_Lynch_20106135"
author: "Kerri Lynch"
date: "2023-01-09"
output: html_document
---

<https://github.com/klynch416/BIOL432_A1>

```{r}

library(ggplot2)
library(dplyr)
source("https://bit.ly/theme_pub")
theme_set(theme_pub())

```


Creates a matrix with 4 columns (Species, Limb_length, Limb_width, Observer) and 100 rows for entries
Randomly sample 100 species/observer names from the given list and assign it to one of the matrix columns
Has a loop run through the matrix one at a time, randomly sample one value within the parameter set for each species name (corresponding with i)

```{r}

source("dataGenerato.R")

```

Read measurements.csv file and create a new column (limb volume) based on the equation for a cylinder using limb length and width
```{r}

source("volumeEstimato.R")

```

Created a table that shows the average limb volume by species and the number of observations each species was recorded by observer
```{r}

measurements <- measurements %>% group_by(Species, Observer, Limb_volume)
avg_vol <- measurements %>% group_by(Species) %>% summarise(mean(Limb_volume))
avg_vol
num_obs <- measurements %>% group_by(Species, Observer) %>% count(Species)
num_obs

```

A single box plot to compare the distributions of limb volumes for each species.
```{r Species_Limb_Volume, fig.cap="Figure 1. Limb volume distribution for five different species; Hydrurga leptonyx (n=23), Setonix brachyurus (n=24),Tyto alba (n=14), Rhincodon typus (n=22), Bison bison (n=17). Limb volume was calculated by ((Limbwidth/2)^2)/Limb length, each of which was recorded by an observer. Shows a potentially statistically significantdifference in limb volume between species."}
ggplot(data = measurements, aes(x = Species, y = Limb_volume)) +
  geom_boxplot() +
  xlab("Limb volume") +
  ylab("Species")

```

A multi-panel plot showing frequency histograms for each species.
```{r Histogram, fig.cap="Figure 2. Limb volume frequency distribution for five different species; Hydrurga leptonyx (n=23), Setonixbrachyurus (n=24), Tyto alba (n=14), Rhincodon typus (n=22), Bison bison (n=17). Limb volume was calculated by((Limb width/2)^2)/Limb length, each of which was recorded by an observer.Shows a potentially statisticallysignificant difference in the distribution of limb volume between species."}
ggplot(data = measurements, aes(x = Limb_volume, fill = Species)) +
  geom_histogram() +
  facet_wrap(~Species) +
  xlab("Limb volume") +
  ylab("Count")

```


